Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of NIRCam Detectors

### 2018-08-30 ms.tex
added pre-amplifier ramp offsets.

JWST has also been considered for observations of temperate Earth-like planets that orbit their stars at a distance where where water could be in liquid form on their surface.
The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
By putting together 30 transits, it may be possible to collect enough photons to detect CO$_2$ and possibly O$_3$ in the atmosphere of TRAPPIST-1 d with JWST \citep{barstow2016trappist1habitable} if clouds have a minimal impact to its atmosphere.
A critical question in studying a planet like TRAPPIST-1 d, however, is whether photon-limited performance is possible with JWST observations.

Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that there many potential systematics that can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.

@@

\subsection{Known Detector Effects}
Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item Intrapixel sensitivity - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item Pre-amp reset offsets (an Asic-related effect) The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
The resets cause discontinuities in the (bias?) level that can be seen on reference pixels.
The NIRCam grism subarrays include reference pixels to mitigate these pre-amp offsets.
	\item 1/f noise - this is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item Even/odd offsets - alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item kTC noise - a random process due to the unknown amount of charge stored at the reset voltage level
\end{itemize}

@@

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{sample_img.pdf}
\caption{Sample Image.}\label{fig:sampFig}
\end{figure}

@@

\begin{figure*}
\gridline{\fig{sample_img.pdf}{0.3\textwidth}{Red Figure}
          \fig{sample_red.png}{0.3\textwidth}{Green Figure}
          }
\caption{Two figures side by side.\label{fig:gridFig}}
\end{figure*}

>>>>

JWST has also been considered for observations of temperate Earth-like planets that orbit their stars at a distance where where water could be in liquid form on their surface.
The TRAPPIST-1 system \citep{gillon2016trappist1Discovery,gillon2017trappist-1sevenp} presents an exciting opportunity to study Earth-sized stars orbiting a 0.1~R$_\odot$ M-type star.
By putting together 10-30 transits, it will be possible to collect enough photons to detect CO$_2$ \citep{barstow2016trappist1habitable,krissansen-totton2018trappist1eJWST} and, optimistically, O$_3$ in the atmosphere of TRAPPIST-1 d with JWST if clouds have a minimal impact to its atmosphere \citep{barstow2016trappist1habitable}.
A critical question in studying a planet like TRAPPIST-1 d, however, is whether photon-limited performance is possible with JWST observations.

Experience with the Hubble Space Telescope (HST), \spitzer, and \kepler\ shows that many systematics can affect high precision time series and prevent photon-limited performance unless corrected for \citep[e.g.][]{beichman2014pasp}.
Many of these effects are detector-related including charge trapping on HST's detector \citep{berta2012flat_gj1214,zhou2017chargeTrap}, intra-pixel sensitivity on the short wavelength bands of \spitzer\ IRAC \citep{moralesCalderon2006LdwarfsWeatherIPC} and sensitivity to pointing jitter with \kepler\footnote{https://keplerscience.arc.nasa.gov/K2/Performance.shtml} \citep{beichman2014pasp}.

@@

\section{Known Detector Effects}
Known detector effects that could affect stability include:
\begin{itemize}[noitemsep]
	\item Intrapixel sensitivity - including sub-pixel flat fielding issues and sub-pixel crosshatching on the detectors \citep{shapiro2018crosshatch}
	\item Pre-amp reset offsets (an Asic-related effect) The NIRCam detectors' pre-amps are reset once per frame (as opposed to once per integration) to prevent large amplifier drifts over an integration \citep{robberto2014refPixPreAmp}.
The resets cause discontinuities in the (bias?) level that can be seen on reference pixels.
The NIRCam grism subarrays include reference pixels to mitigate these pre-amp offsets.
	\item 1/f noise - this is a noise source where most of the noise power is concentrated as low frequencies. 1/f noise causes spatial correlations in the fast-read direction (along detector rows). It is highly correlated between amplifiers, suggesting that it is caused by a common reference voltage. 1/f noise is efficiently removed by reference pixels
	\item Even/odd offsets - alternating columns have different bias levels. Additionally, there are offsets between columns that can change from frame to frame, especially on NIRCam's LW detector
	\item kTC noise - a random process due to the unknown amount of charge stored at the reset voltage level
\end{itemize}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.4\columnwidth]{allamps.pdf}
\caption{Reference pixel time series for a two ramp integration showing pre-amplifier resets.}\label{fig:sampFig}
\end{figure}

allamps.pdf

@@

@@

%\begin{figure*}
%\gridline{\fig{sample_img.pdf}{0.3\textwidth}{Red Figure}
%          \fig{sample_red.png}{0.3\textwidth}{Green Figure}
%          }
%\caption{Two figures side by side.\label{fig:gridFig}}
%\end{figure*}
